---
title: "Plotly"
output: 
  html_document:
    toc: true
    toc_float: true
---

Load the required packages. 
```{r, message=FALSE}
library(tidyverse)
library(p8105.datasets)
library(plotly)
```

We'll will take a closer look at the NYC restaurant inspection data. Only keep the inspections with a grade of A, B, or C and with a score; take a random sample of 5000.
```{r}
data(rest_inspec)

nyc_rest_inspect = 
  rest_inspec %>% 
  filter(grade %in% c("A","B","C")) %>% 
  select(boro, critical_flag, score, zipcode, grade, dba) %>% 
  drop_na(score, grade) %>% 
  sample_n(5000) #takes random sample of 1000
```

### Boxplot  
First, I'm interested in the distribution of scores for each borough so let's create a box plot to see how the scores compare (note: scores are converted into grades, where a lower score earns a higher grade). 
```{r}
nyc_rest_inspect %>% 
  plot_ly(
    x = ~boro, y = ~score, type = "box", color = ~boro)
```
Surpringly, the distributions of scores across the five boroughs are pretty consistent. However, there are a number of outliers. 


### Barplot  
I'm also interested in the likelihood of receiving a critical flag for each borough (according to the data dictionary, critical violations are those most likely to contribute to foodborne illness). Let's create a barplot to see this!  
```{r}
nyc_rest_inspect %>% 
  group_by(boro) %>% 
  summarize(rate_critical = sum(critical_flag == "Critical") / n()) %>% 
  plot_ly(
    x = ~boro, y = ~rate_critical, type = "bar", color = ~boro, colors = "viridis"
  )
```
From the bar plot, we see that the likelihood of receiving a critical flag is about 50% for each of the borough. 

### Scatterplot  
Next, I want to look at the score and grading of "Joe's Shanghai" over the past few years (one of my favorite Chinese restaurant!) I'll create a scatter plot to look at this. 
```{r}
rest_inspec %>% 
  filter(camis == 40548766) %>% 
  drop_na(score, grade) %>%
  mutate(text_label = str_c("Grade: ", grade, 
                            "\nViolation code: ", violation_code)) %>% 
  plot_ly(
    y = ~score, x = ~inspection_date, type = "scatter", mode = "markers",
    text = ~text_label
  )
```

From this simple scatter plot, we see that the scores increased from 2014 (grade=A) to 2016(grade=C), meaning there were increases in violations. However, the restaurant received a grade of A in 2017. Note that you can hover on the data point to see the grade and related violation code. 
